Manuscript

### 2022-02-05 analysis/manuscript.Rmd

boxplot

@@

DT::datatable(paths_summary, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3)

>>>>

boxplot
```

@@

format_round_cols <- c(colnames(dplyr::select(paths_summary, ends_with("_beta"))), "gam_rho_resid")
format_signif_cols <- colnames(dplyr::select(paths_summary, ends_with("_pval")))

DT::datatable(paths_summary, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3) %>%
  formatSignif(columns = format_signif_cols, digits = 3)
